Thermodynamic fragments in magic state theories

### 2021-02-02 magic_paper.tex
Added rates and figures of rates for key noise, temperature regimes. Low temperature looks pretty horrible

The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3\Z_\beta)^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
\end{equation}
The process in~\cref{eq:stdist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} \geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta \Big]}} = \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta F_\beta}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta F_\beta},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
The free energy of thermal state $\gamma_\beta$ is denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] - \beta^{-1} \tr[\gamma_\beta \log{\gamma_\beta}].
\end{equation}

@@

The first elbow of the target state is located at $x'_0 = (2e^{-\beta E_0} / (2\Z_\beta))^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_lowtemp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = 2^n \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{6} - \frac{1}{18}\epsilon' \right)^{\tt}.
\end{equation}
Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:stdist} is possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} - \beta F_\beta + \beta E_{\rm{max}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} - \beta F_\beta + \beta E_{\rm{max}}},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon$.

>>>>

The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = (3\Z_\beta)^{\tt-n} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
\end{equation}
The process in~\cref{eq:msd_thermal} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} \geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta \Big]}} = \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta F_\beta}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta F_\beta},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
The free energy of thermal state $\gamma_\beta$ is denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] - \beta^{-1} \tr[\gamma_\beta \log{\gamma_\beta}].
\end{equation}

Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big( 1-\frac{4}{3}\epsilon \big)}}{\beta F_\beta},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}

@@

The first elbow of the target state is located at $x'_0 = (2e^{-\beta E_0} / (2\Z_\beta))^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_lowtemp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = 2^n \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{6} - \frac{1}{18}\epsilon' \right)^{\tt}.
\end{equation}
Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the distillation process in~\cref{eq:msd_thermal} is possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon$.

We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
It is given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\big(\frac{3}{3-\epsilon} \big)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$. 
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    \nick{Terrible bound for low temperatures. I'll check for possible calculation errors.}
    }
    \label{fig:distill_bounds_lowtemp}
\end{figure}
